Peaks and valleys of prolatin-related gene expression during the pigeon parental care cycle

### 2019-09-05 docs/SICB2020.Rmd
edited

Removal of offspring around the time of hatch time causes prolactin to plummet and gene expression patterns shift to a non-parental state, suggesting an external stimulus-driven response; however prolonging incubation or delaying hatch have a much more subtle effect on gene expression.

@@

By characterizing and manipulating parental care and measuring the effects on hormones and gene expression in both male and female parents over time, we provide a deeper understanding of how the hypothalamic-pituitary-gonadal axis responds to predictable and unpredictable changes during offspring development.

>>>>

Removal of offspring around the time of chicks hatching causes circulating prolactin to plummet and gene expression patterns shift to a non-parental state, suggesting an external stimulus-driven response; however prolonging incubation or delaying hatch have a much more subtle effect on gene expression.

@@

By characterizing and manipulating parental care and measuring the effects on hormones and gene expression in both male and female parents over time, we provide a more complete picture of how the hypothalamic-pituitary-gonadal axis responds to predictable and unpredictable changes during offspring development.
